\Large{Holier Than Thou? No Partisan Gap in the Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}. }

### 2023-01-05 ms/adult.tex
Update ms
Add tables for pornography consumption for Independents vs partisans (D/R) in the SI. Also added the corresponding footnote into the main text. And some other minor formatting changes.

@@

\title{\Large{Holier Than Thou? No Partisan Gap in the Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}}

@@

\section*{Data}\label{sec:data}
We use data from YouGov to measure the consumption of adult content \citep{data-dataverse}. YouGov maintains a large panel that is recruits using various methods. YouGov uses matched sampling to survey respondents: it first draws a random sample from a large synthetic representative sampling frame, finds respondents that match the sampled individuals from its panel, and invites them to take a survey. For data on how well Yougov is able to approximate a random sample, see \citet{rivers2009}. For our sample, panelists also shared de-identified web browsing data tracked via passive metering software installed voluntarily on their computers. The software, called RealityMine, captures online visits independent of the type of browser or browser-specific privacy settings.

@@

\section*{Measuring Pornographic Content}
We code pornographic content at the domain level. Our main analysis depends on the domain classifications that come with YouGov data. We code domains that YouGov categorizes as ``Adult'' as pornographic sites. These include ``Adult'' (e.g., xvideos.com), ``Adult, Business'' (e.g., onlyfans.com), and ``Adult, Entertainment'' (e.g., hentainfox.com). Yougoc classifies certain domains as 'Adult' that do not primarily carry pornographic content, e.g., urbandictionary.com and 4chan.org . Given the skew in the data (See \cref{fig:top25_adult} and \cref{fig:top25_nonadult})\footnote{We use the \texttt{forestplot} \citep{forestplot} and \texttt{tableone} \citep{tableone} packages to tabulate key descriptive figures.}, we manually check the top adult domains to remove such sites. If there is graphic nudity on the landing page or if the site is some form of erotica, we classify the site as a pornographic.

@@

\section*{Results}

@@

The consumption of pornography is also highly concentrated among a few sites, with ten most frequented pornography sites receiving more than 12 times the traffic to all other pornographic sites  (approximately 109 minutes vs. 9 minutes, see \cref{fig:concentration_porn_consumption}). Close to 80 percent of the traffic to pornographic sites is to just one pornographic site. Looking at the characteristics of consumers of pornography, expectedly, consumers of pornography online are younger and are more likely to be male \cref{fig:} %TODO

@@

Given the skew in the data, we ran a quantile regression, regressing the duration on party. As Figures \ref{fig:quantile_regression_duration} and \ref{fig:quantile_regression_prop_duration} show, there are no significant differences in consumption of pornographic content between the parties. To account for the possibility that this may be a result of confounding demographic differences between the parties, we control for immutable characteristics like age and gender. (\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.) We use these variables in our analyses of pornography consumption below. Given how concentrated pornographic consumption is in our data, it is unlikely to make much of a difference and that is indeed what we find --- see Figure \ref{fig:quantile_regression_duration}. 
%===========================
% Quantile regressions
% Hours spent on adult sites
%===========================
\begin{figure}[t]
	\centering
	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party}
	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
	}
	\label{fig:quantile_regression_duration}
\end{figure}

@@

\section*{Discussion}

Consumption of pornography has been attributed to a variety of ills. It is also considered problematic from a religious perspective. For instance, Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}}. The Internet has dramatically increased access to pornography. This has led to the concern that pornography consumption has become very widespread and extensive. Our data suggest that pornography consumption online is highly concentrated with very few people consuming a lot of pornography and most people consuming very little or none.

@@

%===============================================================================
%===============================================================================
% Appendix
%===============================================================================
%===============================================================================
\appendix
\renewcommand{\thesection}{SI \arabic{section}}
\renewcommand\thetable{\thesection.\arabic{table}}  
\renewcommand\thefigure{\thesection.\arabic{figure}}
\counterwithin{figure}{section}
\counterwithin{table}{section}
\begin{center}
\Large{Supporting Information}
\end{center}

\FloatBarrier
%===============================================================================
% Supplementary Descriptives for sense of landscape of porn consumption
%===============================================================================
\section{Descriptive Analysis}

\subsection{Skew in Website Visits}
%============================
% Figure of top 25 adultsites
%============================
\begin{figure}[ht]
	\centering
	\caption{Top 25 Pornography Sites}
	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows the top 25 pornographic sites that individuals visit in the sample period.
		Pornography sites are as categorized by YouGov (see the \nameref{sec:data} section).
		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  
		Sites to the right of the vertical dashed are the top 1 percent of pornographic sites.
	}
	\label{fig:top25_adult}
\end{figure}

@@

\FloatBarrier
\subsection{Skew in Consumption of Pornographic Content}
%====================================================
% Tabulated percentiles of hours spent on adult sites
%====================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online}
	\label{tab:distribution_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{cr}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		%See \cref{fig:distribution_duration} for the plot.
	}
\end{table}

@@

\FloatBarrier
\section{Partisan Differences}
\subsection{Distribution of Differences}
%===========================================================================
% Tabulated splits by party and by percentiles for hours spent on adultsites
%===========================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online by Party}
	\label{tab:distribution_duration_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Hours}}\\
			\cmidrule(l){2-3}
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		%See \cref{fig:distribution_duration_party} for the plot.
	}
\end{table}

%===============================================================================
% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
%===============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Time Spent on Pornographic Sites by Party}
	\label{tab:distribution_prop_duration_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
			\cmidrule(l){2-3}
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		%See \cref{fig:distribution_prop_duration_party} for the plot.
	}
\end{table}

\FloatBarrier
\subsection{Accounting for Confounders}
%==============================================================================
% Table for balance of porn consumption and individual characteristics by party
%==============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
	\caption{Differences in Pornography Consumption and Individual Characteristics by Party}
	\label{tab:characteristics_split_by_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_outcomes_by_party.tex}\\
			%-------------------------------------------------------------------
			\cmidrule{2-8}
			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_covariates_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\scriptsize \emph{Notes:}
		Table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) shows subgroups for categorical variables.
		Column (2) indicates the count of missing variables, if any.
		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, Democratic individuals, and Republican individuals.
		Standard deviations and percentages in parentheses.
		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
		Given the skew in consumption of pornography, we also performed tests for difference in means for the measures of pornography consumption by party. See \cref{tab:characteristics_split_by_party_medians}.
	}
\end{table}

@@

\FloatBarrier
%===============================================================================
% Consequence of Using Alternate Ways of Measuring Pornography and Alternative Analyses on Time Spent on Pornography
%===============================================================================
\section{Alternate Ways of Measuring Pornography}
\label{si:alternate_ways}
\clearpage

\section{Consumption of Pornography Among Independents}

\FloatBarrier
\section{Alternate Measures}
%============================================================================
% Figure of porn consumption by party
% Y-axis = proportion of individuals that ever consumed porn in sample period
%============================================================================

\subsection{Proportion of Partisans Who Consumed Any Pornography}
\begin{figure}
	\centering
	\caption{Pornography Consumption by Party}
	\includegraphics[width=.5\textwidth]{../figs/consume_porn_yes_no.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows proportion of individuals in the sample who ever consumed pornography in the sample period by party.
		Capped vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:consume_porn_yes_no}
\end{figure}
\clearpage

\FloatBarrier
%===============================================================================
%===============================================================================
% Analogous results for visits to adult sites
%===============================================================================
%===============================================================================
\subsection{Analyses of Visits}
\label{si:visits}
%=================================================
% Figure for Distribution of visits to adult sites
%=================================================
\begin{figure}[ht]
	\centering
	\caption{Distribution of Traffic to Pornography Online}
	\includegraphics[width=.5\linewidth]{../figs/distribution_visits_to_adultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows the number of visits to pornography sites by individuals who consumed pornography in the sample period.
		Individuals are split into deciles with each bin containing approximately the same number of individuals.
		Height of bars indicate mean of each bin.
		Capped vertical bars are 95\% confidence intervals.
		%See \cref{tab:distribution_visits} for the more tabulated values.
	}
	\label{fig:distribution_visits}
\end{figure}

>>>>

\usepackage{tocloft}

@@

\title{\Large{Holier Than Thou? No Partisan Gap in the Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}.
		%We thank Alexander Marsolais (YouGov) and Rajashekar Chintalapati. 
	}
}

@@

\section*{Data}\label{sec:data}
\addcontentsline{toc}{section}{\nameref{sec:data}}
We use data from YouGov to measure the consumption of adult content \citep{data-dataverse}. YouGov maintains a large panel that is recruits using various methods. YouGov uses matched sampling to survey respondents: it first draws a random sample from a large synthetic representative sampling frame, finds respondents that match the sampled individuals from its panel, and invites them to take a survey. For data on how well Yougov is able to approximate a random sample, see \citet{rivers2009}. For our sample, panelists also shared de-identified web browsing data tracked via passive metering software installed voluntarily on their computers. The software, called RealityMine, captures online visits independent of the type of browser or browser-specific privacy settings.

@@

\section*{Measuring Pornographic Content}\label{sec:measuring_porn_content}
\addcontentsline{toc}{section}{\nameref{sec:measuring_porn_content}}

We code pornographic content at the domain level. Our main analysis depends on the domain classifications that come with YouGov data. We code domains that YouGov categorizes as ``Adult'' as pornographic sites. These include ``Adult'' (e.g., xvideos.com), ``Adult, Business'' (e.g., onlyfans.com), and ``Adult, Entertainment'' (e.g., hentainfox.com). Yougov classifies certain domains as 'Adult' that do not primarily carry pornographic content, e.g., urbandictionary.com and 4chan.org . Given the skew in the data (See \cref{fig:top25_adult} and \cref{fig:top25_nonadult})\footnote{We use the \texttt{forestplot} \citep{forestplot} and \texttt{tableone} \citep{tableone} packages to tabulate key descriptive figures.}, we manually check the top adult domains to remove such sites. If there is graphic nudity on the landing page or if the site is some form of erotica, we classify the site as a pornographic.

@@

\section*{Results}\label{sec:results}
\addcontentsline{toc}{section}{\nameref{sec:results}}

@@

The consumption of pornography is also highly concentrated among a few sites, with ten most frequented pornography sites receiving more than 12 times the traffic to all other pornographic sites  (approximately 109 minutes vs. 9 minutes, see \cref{fig:concentration_porn_consumption}). Close to 80 percent of the traffic to pornographic sites is to just one pornographic site. Looking at the characteristics of consumers of pornography, expectedly, consumers of pornography online are younger and are more likely to be male (see, for instance, Panel B of \cref{tab:characteristics_split_by_porn_consumers}).

@@

Given the skew in the data, we ran a quantile regression, regressing the duration on party. As Figures \ref{fig:quantile_regression_duration} and \ref{fig:quantile_regression_prop_duration} show, there are no significant differences in consumption of pornographic content between the parties. To account for the possibility that this may be a result of confounding demographic differences between the parties, we control for immutable characteristics like age and gender. (\cref{tab:characteristics_split_by_party} shows differences in age, gender, and race by party identification.) We use these variables in our analyses of pornography consumption below. Given how concentrated pornographic consumption is in our data, it is unlikely to make much of a difference and that is indeed what we find --- see Figure \ref{fig:quantile_regression_duration}.\footnote{
	We also investigated consumption of pornography among independents in \cref{si:independents}.
	At the median, Independents consume more pornography compared to partisans in terms of the amount of time spent and the percentage of time spent on pornography online (1.3 hours vs 0.7 hours in \cref{tab:percentiles_duration_adultsites_by_individuals_independents_partisans} and 3.4\% vs 2.3\% in \cref{tab:percentiles_prop_duration_adultsites_by_individuals_independents_partisans}).
	This difference is driven by the relatively higher consumption of pornography among Republicans.

	This pattern reverses somewhat near the right tail  of the distribution.
	Independents also consume more pornography at the right tail of the distribution. 
	At the 95th percentile, Independents consume about 3.5 hours more and spend 13.9\% more of their internet browsing time on pornography online.
	This behavior at the right tail is driven by the relatively higher consumption of pornography among the Democrats.
}

%===========================
% Quantile regressions
% Hours spent on adult sites
%===========================
\begin{figure}[t]
	\centering
	\caption{Quantile Estimates--Hours Spent on Pornographic Sites by Party}
	\includegraphics[width=.7\linewidth]{../figs/quantile_reg_duration_adult.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Dependent variable is the number of hours individuals in our sample spent on pornographic sites.
		Each point indicates the difference between Republicans and Democrats and corresponds to a quantile regression at the quantile indicated by the x-axis.
		95\% confidence intervals constructed from standard errors.
		See \cref{fig:quantile_regression_duration_covariates} for the same plot controlling for individual characteristics.
	}
	\label{fig:quantile_regression_duration}
\end{figure}

@@

\section*{Discussion}\label{sec:discussion}
\addcontentsline{toc}{section}{\nameref{sec:discussion}}
Consumption of pornography has been attributed to a variety of ills. It is also considered problematic from a religious perspective. For instance, Christian theologians believe that consumption of pornography leads people away from purity and hence should be avoided.\footnote{\url{https://www.churchofjesuschrist.org/study/manual/help-for-pornography-users/effect-of-pornography}} The Internet has dramatically increased access to pornography. This has led to the concern that pornography consumption has become very widespread and extensive. Our data suggest that pornography consumption online is highly concentrated with very few people consuming a lot of pornography and most people consuming very little or none.

@@

%===============================================================================
%===============================================================================
% Appendix
%===============================================================================
%===============================================================================
\appendix
\renewcommand{\thesection}{SI \arabic{section}}
\renewcommand\thetable{\thesection.\arabic{table}}  
\renewcommand\thefigure{\thesection.\arabic{figure}}
\counterwithin{figure}{section}
\counterwithin{table}{section}

\section{Supporting Information}\label{si}
%\begin{center}
%\Large{Supporting Information}
%\end{center}

\FloatBarrier
%===============================================================================
% Supplementary Descriptives for sense of landscape of porn consumption
%===============================================================================
\subsection{Descriptive Analysis}

\subsubsection{Skew in Website Visits}
%============================
% Figure of top 25 adultsites
%============================
\begin{figure}[ht]
	\centering
	\caption{Top 25 Pornography Sites}
	\includegraphics[width=\textwidth]{../figs/top_25_adultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows the top 25 pornographic sites that individuals visit in the sample period.
		Pornography sites are as categorized by YouGov (see the \nameref{sec:data} section).
		The \emph{Hours} column are the total number of hours that individuals in the sample spent on the site. 
		The \emph{Visits} column is total number of visits by individuals in the sample to the site.  
		Sites to the right of the vertical dashed are the top 1 percent of pornographic sites.
	}
	\label{fig:top25_adult}
\end{figure}

@@

\FloatBarrier
\subsubsection{Skew in Consumption of Pornographic Content}
%====================================================
% Tabulated percentiles of hours spent on adult sites
%====================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online}
	\label{tab:distribution_duration}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{cr}
			\toprule
			\multicolumn{1}{c}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Hours}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows key percentiles (each of the ten deciles plus quantiles at the right tail) and their corresponding values for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		%See \cref{fig:distribution_duration} for the plot.
	}
\end{table}

@@

\FloatBarrier
\subsection{Partisan Differences}
\subsubsection{Distribution of Differences}
%===========================================================================
% Tabulated splits by party and by percentiles for hours spent on adultsites
%===========================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Distribution of Consumption of Pornography Online by Party}
	\label{tab:distribution_duration_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{Hours}}\\
			\cmidrule(l){2-3}
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		%See \cref{fig:distribution_duration_party} for the plot.
	}
\end{table}

%===============================================================================
% Tabulated splits by party and by percentiles for proportion of time spent on adultsites
%===============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{10 pt}
	\caption{Percentage of Time Spent on Pornographic Sites by Party}
	\label{tab:distribution_prop_duration_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{crr}
			\toprule
			\multicolumn{1}{l}{\textbf{}}&\multicolumn{2}{c}{\textbf{\% time}}\\
			\cmidrule(l){2-3}
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}\\
			\midrule
			\input{../tabs/percentiles_proportion_duration_adultsites_by_individuals_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by party and by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period. 
		%See \cref{fig:distribution_prop_duration_party} for the plot.
	}
\end{table}

\FloatBarrier
\subsubsection{Accounting for Confounders}
%==============================================================================
% Table for balance of porn consumption and individual characteristics by party
%==============================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{5 pt}
	\caption{Differences in Pornography Consumption and Individual Characteristics by Party}
	\label{tab:characteristics_split_by_party}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}llrcccrr@{\hspace{0\tabcolsep}}}
			\toprule
			&\multicolumn{7}{c}{\underline{Panel A. Measures of pornography consumption}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_outcomes_by_party.tex}\\
			%-------------------------------------------------------------------
			\cmidrule{2-8}
			&\multicolumn{7}{c}{\underline{Panel B. Individual characteristics}}\\
			&\multicolumn{1}{l}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}&\multicolumn{1}{c}{(6)}&\multicolumn{1}{r}{(7)}\\			
			&\multicolumn{1}{l}{Subgroups}&\multicolumn{1}{c}{NA}&\multicolumn{1}{c}{Total}&\multicolumn{1}{c}{Democrat}&\multicolumn{1}{c}{Republican}&\multicolumn{1}{c}{P-val}&\multicolumn{1}{r}{SMD}\\
			\cmidrule{2-8}
			\input{../tabs/balance_covariates_by_party.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\scriptsize \emph{Notes:}
		Table shows splits by party for pornography consumption and for individual characteristics for the 1,200 individuals.
		Party identification is based on a 7-point scale. We code 1--3 as ``Democrat'', 4 as ``Independent'', 5--7 as ``Republican''.
		Column (1) shows subgroups for categorical variables.
		Column (2) indicates the count of missing variables, if any.
		Columns (3)--(5) show means and standard deviations for continuous variables and count and percentage of data for categorical variables, for the full sample, Democratic individuals, and Republican individuals.
		Standard deviations and percentages in parentheses.
		Column (6) and column (7) report the p-values and standardized mean differences for Democrats vs Republicans.
		Given the skew in consumption of pornography, we also performed tests for difference in means for the measures of pornography consumption by party. See \cref{tab:characteristics_split_by_party_medians}.
	}
\end{table}

@@

\FloatBarrier
%===============================================================================
% Consequence of Using Alternate Ways of Measuring Pornography and Alternative Analyses on Time Spent on Pornography
%===============================================================================
\subsection{Alternate Ways of Measuring Pornography}
\label{si:alternate_ways}
\clearpage

\subsection{Consumption of Pornography Among Independents}
\label{si:independents}
%===========================================================================
% Tabulated splits by party and by percentiles for hours spent on adultsites
%===========================================================================
\begin{table}[ht] \centering \small \setlength\tabcolsep{6 pt}
	\caption{Distribution of Consumption of Pornography Online Among Independents}
	\label{tab:percentiles_duration_adultsites_by_individuals_independents_partisans}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}crrrrr@{\hspace{0\tabcolsep}}}
			\toprule		
			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}\\	
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}&\multicolumn{1}{c}{\textbf{Partisans}}&\multicolumn{1}{c}{\textbf{Independents}}&\multicolumn{1}{r}{\textbf{Independents/DK}}\\
			\midrule
			\input{../tabs/percentiles_duration_adultsites_by_individuals_independents_partisans.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the duration (hours) spent by individuals who consumed pornography in the sample period. 
		Column (1) includes Democrats (n = 154).
		Column (2) includes Republicans (n = 95).
		Column (3) includes both Republicans and Democrats (n = 249).
		Column (4) includes Independents (n = 67).
		Column (5) includes Independents, those who report ``Don't Know'' for partisan identification, and those who do not report (n = 104).
		%See \cref{fig:distribution_duration_party} for the plot.
	}
\end{table}

\begin{table}[ht] \centering \small \setlength\tabcolsep{6 pt}
	\caption{Percentage of Time Spent on Pornographic Sites Among Independents}
	\label{tab:percentiles_prop_duration_adultsites_by_individuals_independents_partisans}
	\begin{adjustbox}{max width=\textwidth}
		\begin{tabular}{@{\hspace{0\tabcolsep}}crrrrr@{\hspace{0\tabcolsep}}}
			\toprule		
			&\multicolumn{1}{c}{(1)}&\multicolumn{1}{c}{(2)}&\multicolumn{1}{c}{(3)}&\multicolumn{1}{c}{(4)}&\multicolumn{1}{c}{(5)}\\	
			\multicolumn{1}{l}{\textbf{Percentile}}&\multicolumn{1}{c}{\textbf{Republicans}}&\multicolumn{1}{c}{\textbf{Democrats}}&\multicolumn{1}{c}{\textbf{Partisans}}&\multicolumn{1}{c}{\textbf{Independents}}&\multicolumn{1}{r}{\textbf{Independents/DK}}\\
			\midrule
			\input{../tabs/percentiles_prop_duration_adultsites_by_individuals_independents_partisans.tex}\\
			\bottomrule
		\end{tabular}
	\end{adjustbox}
	\caption*{\footnotesize \emph{Notes:} 
		Table shows splits by partisans and non-partisans, by key percentiles (each of the ten deciles plus quantiles at the right tail) for the percentage of time spent on pornography by individuals who consumed pornography in the sample period. 
		Column (1) includes Democrats (n = 154).
		Column (2) includes Republicans (n = 95).
		Column (3) includes both Republicans and Democrats (n = 249).
		Column (4) includes Independents (n = 67).
		Column (5) includes Independents, those who report ``Don't Know'' for partisan identification, and those who do not report (n = 104).
		%See \cref{fig:distribution_duration_party} for the plot.
	}
\end{table}

\FloatBarrier
\subsection{Alternate Measures}
%============================================================================
% Figure of porn consumption by party
% Y-axis = proportion of individuals that ever consumed porn in sample period
%============================================================================

\subsubsection{Proportion of Partisans Who Consumed Any Pornography}
\begin{figure}
	\centering
	\caption{Pornography Consumption by Party}
	\includegraphics[width=.5\textwidth]{../figs/consume_porn_yes_no.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows proportion of individuals in the sample who ever consumed pornography in the sample period by party.
		Capped vertical bars are 95\% confidence intervals from bootstrapped standard errors (n = 1,000).
	}
	\label{fig:consume_porn_yes_no}
\end{figure}
\clearpage

\FloatBarrier
%===============================================================================
%===============================================================================
% Analogous results for visits to adult sites
%===============================================================================
%===============================================================================
\subsubsection{Analyses of Visits}
\label{si:visits}
%=================================================
% Figure for Distribution of visits to adult sites
%=================================================
\begin{figure}[ht]
	\centering
	\caption{Distribution of Traffic to Pornography Online}
	\includegraphics[width=.5\linewidth]{../figs/distribution_visits_to_adultsites.pdf}
	\caption*{\footnotesize \emph{Notes:} 
		Figure shows the number of visits to pornography sites by individuals who consumed pornography in the sample period.
		Individuals are split into deciles with each bin containing approximately the same number of individuals.
		Height of bars indicate mean of each bin.
		Capped vertical bars are 95\% confidence intervals.
		%See \cref{tab:distribution_visits} for the more tabulated values.
	}
	\label{fig:distribution_visits}
\end{figure}
